---
title: "hw01_gapminder"
author: "sdhanani"
date: "September 15, 2017"
output: github_document
---
```{r}
library(tidyverse)
library(gapminder)
str(gapminder)
head(gapminder)
nrow(gapminder)
ncol(gapminder)
```
Now we've loaded the packages and took intial looks at the data through thet structure and the top 6 rows of the data. Inspected the data and found the number of rows and columns. 

Would be curious to see what the range of the numeric values are:
```{r}
range(gapminder$year)
range(gapminder$lifeExp)
range(gapminder$pop)
range(gapminder$gdpPercap)
```

Want to see general summary of all the variables in the gapminder dataset:
```{r}
summary(gapminder$country)
summary(gapminder$continent)
summary(gapminder$year)
summary(gapminder$lifeExp)
summary(gapminder$pop)
summary(gapminder$gdpPercap)
```
Some preliminary plotting of numeric variables
```{r}
plot(lifeExp~year, data=gapminder)
```
```{r}
plot(gdpPercap~year, gapminder)
```
```{r}
plot(lifeExp~pop, gapminder)
```

Some plots of numeric and categorical variables
```{r}
boxplot(lifeExp~continent, gapminder)
boxplot(gdpPercap~continent, gapminder)
```
